### 2021-09-07 input/proposal.tex
wip on proof

\begin{theorem}[\label{theo:threephase}Three-phase purge]
  The following three phases are sufficient to eventually purge the
  system from stale control information:
  \begin{inparaenum}[(i)]
  \item propagation of delete notifications,
  \item detection of possibly blocking conditions, and
  \item propagation of possibly deleted but blocked notifications.
  \end{inparaenum}
\end{theorem}

@@

\begin{proof}
  Figure~\ref{fig:proofB} depicts all possible cases that need
  appropriate purging. A chain of \processes $[a, b, c, d]$ delivered
  and forwarded a message $\alpha_X$. Some \processes may have
  delivered messages about other partitions before or after
  $\alpha_X$.
  \begin{asparadesc}
  \item [\processes with last $\alpha_X$:] \Processes such as $a$
    where the last and best partition is still $P_X$. By propagating
    from \process to \process the corresponding $\delta_X$ message,
    these \processes purge $\alpha_X$.
  \item [\processes with $\alpha_X^x \rightarrow \alpha_Y^y$ with last
    $\alpha_Y^y$, for $\alpha_Y^y< \alpha_X^x$:] \Processes such as
    \Process~$b$ that do not directly suffer from the non-delivery of
    $\delta_X$. They need to purge their own $P_Y$ if need
    be. Nonetheless, they deliver and forward $\alpha_Y$ that at least
    one following \process will receive.
  \item [\processes with $\delta_Y \rightarrow \alpha_X$:] \Processes
    such as \Process~$c$ that do not belong to the preceding category,
    for they already delivered $\delta_Y$. Nevertheless, best eventual
    forwarding guarantees that they receive $\alpha_Y$, which
    contradicts their history or state. In such a case, the detecting
    \processes purge their own $\alpha_X$. The detecting \processes
    must also notify subsequent \processes that their current
    partition \emph{may be} deleted. Indeed their parent may have
    blocked the corresponding $\delta$ messages and subsequent
    \processes must purge their possibly stale state, for the sake of
    consistency.  We note such a notification $\Delta_X$ to emphasize
    their proximity to $\delta_X$ messages.
    % the uncertainty of a $\delta$ message.
  \item [\processes with last $\alpha_X$ receiving $\Delta_X$ from
    their parent:] \Processes such as \Process~$d$ that have
    $\alpha_X$ but preceding delivered messages are not
    important. Such \processes must trust detecting \processes by
    delivering and forwarding $\Delta_X$. It is worth noting that
    these messages are subject to all aforementioned blocking
    conditions, but are also solved by aforementioned mechanisms.
  \end{asparadesc}

>>>>

\begin{theorem}[\label{theo:threephase}\TODO{Three-phase purge}]
  The following three phases are sufficient to eventually purge the
  system from stale control information:
  \begin{inparaenum}[(i)]
  \item propagation of delete notifications,
  \item detection of possibly blocking conditions, and
  \item propagation of possibly deleted but blocked notifications.
  \end{inparaenum}
\end{theorem}

@@

\begin{proof}
  Figure~\ref{fig:proofB} depicts all possible cases that need
  appropriate purging. A chain of \processes $[a, b, c, d]$ delivered
  and forwarded a message $\alpha_X$. Some \processes may have
  delivered messages about other partitions before or after
  $\alpha_X$. \Processes such as $a$ and $d$ have delivered unrelated
  messages, but their last message is about $P_X$: $d_a(\_)
  \rightarrow \ldots \rightarrow d_a(\alpha_X)$; \Processes such as $b$
  and $c$ delivered messages about $P_X$ and $P_Y$ in different order;
  For \processes such as $b$, the last delivery is $\alpha_Y$:
  $d_b(\_) \rightarrow \ldots \rightarrow d_b(\alpha_X) \rightarrow
  \ldots \rightarrow d_b(\alpha_Y)$; For \processes such as $c$, the
  last delivery is a stale $\alpha_X$, but they delivered the addition
  and removal of $P_Y$: $d_c(\_) \rightarrow \ldots \rightarrow
  d_c(\alpha_Y) \rightarrow \ldots \rightarrow d_c(\delta_Y)
  \rightarrow \ldots \rightarrow d_c(\alpha_X)$.

  \begin{asparadesc}
  \item [\TODO{source is type $a$}]
  \item [($a$ or $c$ or $d$) to ($a$ or $c$ or $d$):] By propagating
    from \process to \process the corresponding $\delta_X$ message,
    these \processes purge $\alpha_X$.
  \item [$a$ to $b$:] $b$ stops the propagation of $\delta_X$, for the
    latter does not target its current partition.
  \item [$b$:] They need to purge their own $P_Y$, we must \TODO{prove
    that $[a, b, c, d]$ is solved and that it does not require to
    purge $P_Y$.}
  \item [$b$ to $d$:] would deliver $d_(\alpha_y)$ hence becoming $b$.
  \item [$b$ to $c$:] block $d_c(\alpha_y)$, so $c$ stays in $c$. But
    it detects $b$ is its parent, and possibly blocked any delta with
    its value $r_b(\delta_z) \rightarrow d_b(\delta_z)$. Since not
    sure, $\Delta$

  \item [\processes with $\alpha_X^x \rightarrow \alpha_Y^y$ with last
    $\alpha_Y^y$, for $\alpha_Y^y< \alpha_X^x$:] \Processes such as
    \Process~$b$ that do not directly suffer from the non-delivery of
    $\delta_X$. They need to purge their own $P_Y$ if need
    be. Nonetheless, they deliver and forward $\alpha_Y$ that at least
    one following \process will receive.
  \item [\processes with $\delta_Y \rightarrow \alpha_X$:] \Processes
    such as \Process~$c$ that do not belong to the preceding category,
    for they already delivered $\delta_Y$. Nevertheless, best eventual
    forwarding guarantees that they receive $\alpha_Y$, which
    contradicts their history or state. In such a case, the detecting
    \processes purge their own $\alpha_X$. The detecting \processes
    must also notify subsequent \processes that their current
    partition \emph{may be} deleted. Indeed their parent may have
    blocked the corresponding $\delta$ messages and subsequent
    \processes must purge their possibly stale state, for the sake of
    consistency.  We note such a notification $\Delta_X$ to emphasize
    their proximity to $\delta_X$ messages.
    % the uncertainty of a $\delta$ message.
  \item [\processes with last $\alpha_X$ receiving $\Delta_X$ from
    their parent:] \Processes such as \Process~$d$ that have
    $\alpha_X$ but preceding delivered messages are not
    important. Such \processes must trust detecting \processes by
    delivering and forwarding $\Delta_X$. It is worth noting that
    these messages are subject to all aforementioned blocking
    conditions, but are also solved by aforementioned mechanisms.
  \end{asparadesc}

### 2021-09-07 input/related_work.tex
wip on proof

\noindent Distributing this index among \processes circumvents these
issues~\cite{voronet, ipfs, mdht, squirrel, coin_19}, but still raises
locality issues where \processes
\begin{inparaenum}[(i)]
\item request to a possibly far away location service the content
  location, and then
\item request the actual content from far away replicas.
\end{inparaenum}
For instance, using \underline{d}istributed \underline{h}ash
\underline{t}ables (DHT)~\cite{ipfs, mdht, squirrel}, each \process
stores a part of the index defined by an interval between hash values.
The hash values are the keys to retrieve the associated content
location.  Before downloading any content, a \node asks for its
location using its key. After a series of round-trips between possibly
distant DHT servers, the \node gets a list of available
replicas. Contrarily to \NAME, such services do not ensure to include
the closest replica.

>>>>

\noindent \TODO{CDN in this category?=>} Distributing this index among
\processes circumvents these issues~\cite{voronet, ipfs, mdht,
  squirrel, coin_19}, but still raises locality issues where
\processes
\begin{inparaenum}[(i)]
\item request to a possibly far away location service the content
  location, and then
\item request the actual content from far away replicas.
\end{inparaenum}
For instance, using \underline{d}istributed \underline{h}ash
\underline{t}ables (DHT)~\cite{ipfs, mdht, squirrel}, each \process
stores a part of the index defined by an interval between hash values.
The hash values are the keys to retrieve the associated content
location.  Before downloading any content, a \node asks for its
location using its key. After a series of round-trips between possibly
distant DHT servers, the \node gets a list of available
replicas. Contrarily to \NAME, such services do not ensure to include
the closest replica.
